Approximation as Differentiation

### 2025-04-15 appendix/notes/cmon-enriched.tex
Enriched Yoneda lemma.

$\CMon$ is closed monoidal, with the trivial one-element monoid $\One$ as terminal object and monoidal product
$A \tensor B$ given by the Cartesian product $A \times B$. $\CMon$ is complete and cocomplete, inheriting all
limits and colimits from $\Set$.

@@

Because $\CMon$ is closed monoidal, it is enriched over itself; every hom-object $\Hom{\CMon}{A}{B}$ is a
commutative monoid where:

@@

\noindent Now suppose $\cat{C}$ is $\mathscr{V}$-enriched with $\mathscr{V}$ closed monoidal; then the
hom-functor $\Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$ is itself $\mathscr{V}$-enriched. The

@@

\noindent \todo{Then there is an enriched version of the Yoneda embedding, namely a functor
$\Yoneda_{\mathscr{V}}: \cat{C} \to \Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}$ analogous to $\Yoneda$
which is itself $\mathscr{V}$-enriched.}

>>>>

$\CMon$ is monoidal closed, with the trivial one-element monoid $\One$ as terminal object and monoidal product
$A \tensor B$ given by the Cartesian product $A \times B$. $\CMon$ is complete and cocomplete, inheriting all
limits and colimits from $\Set$.

@@

Because $\CMon$ is monoidal closed, it is enriched over itself; every hom-object $\Hom{\CMon}{A}{B}$ is a
commutative monoid where:

@@

\noindent Now suppose $\cat{C}$ is $\mathscr{V}$-enriched with $\mathscr{V}$ monoidal closed; then the
hom-functor $\Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$ is itself $\mathscr{V}$-enriched. The

@@

\noindent We then have an enriched version of the Yoneda embedding, namely a functor $\Yoneda_{\mathscr{V}}:
\cat{C} \to \Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}$ which sends:

\begin{itemize}
\item each object $X$ in $\cat{C}$ to the enriched hom-functor $\Yoneda_{\mathscr{V}}(X) =
\Hom{\cat{C}}{-}{X}: \cat{C}^\op \to \mathscr{V}$
\item each morphism $f: X \to Y$ in $\cat{C}$ to the natural transformation $\Yoneda_{\mathscr{V}}(f)$ where
$\Yoneda_{\mathscr{V}}(f)_Z$ is again $(f \comp -): \Hom{\cat{C}}{Z}{X} \to \Hom{\cat{C}}{Z}{Y}$
\end{itemize}

\noindent and an enriched Yoneda lemma which says that for any $\mathscr{V}$-enriched presheaf $F$ and any
object $X \in \cat{C}$ the hom-object of natural transformations between the $\mathscr{V}$-enriched presheaf
$\Hom{\cat{C}}{-}{X}$ and $F$, which also lives in $\mathscr{V}$, is isomorphic to $F(X)$:

\begin{lemma}
Suppose $\cat{C}$ is $\mathscr{V}$-enriched with $\mathscr{V}$ monoidal closed. For any $F: \cat{C}^\op \to
\mathscr{V}$ and any object $X$ in $\cat{C}$:
\[\Hom{\Func{\cat{C}^\op}{\mathscr{V}}_{\mathscr{V}}}{\Hom{\cat{C}}{-}{X}}{F} \iso F(X)\]
\end{lemma}
